Automatic prostate cancer detection through \acs*{dce}-\acs*{mri} images: all you need is a good normalization

### 2016-08-27 01_introduction/introduction.tex
remove some highlights

{\color{red}The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.}

>>>>

The benefit of our approach will be shown while using quantitative and semi-quantitative approaches.
Additionally, we show that using the whole normalized \ac{dce}-\ac{mri} signal is preferable to quantitative and semi-quantitative methods, leading to the best classification performance.
